---
title: "Step 3 graphs and options"
author: "Jackie Ouzman"
date: "12 August 2019"
output: html_document
---

```{r setup and install load packages, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)


library(tidyverse)
library(dplyr)
library(lubridate)
library(readxl)

library(ggplot2)
library(readr)
library(sp)
library(biogeo)
library(stringr)
library(rgdal)
library(sf)

library(gganimate)
library(png)
library(gifski)
```

#I need to view specfic days 
I have done this using the filter function and then check out the distance from fence.

Day 1 20/5/2019
Fence 1 and 2
Bring in the data from the data import and cleaning R markdown file

```{r load in the data, echo=FALSE, message=FALSE, warning=FALSE}
Check_df_VF_week1_2_3_InclusionBord_c_animalID <- read_rds("W:/VF/Eden_Valley/logged_VF_data/download2_R_output/df_VF_week1_2_3_InclusionBord_c_animalID_clean.rds")

eden_valley <- st_read(
  "W:/VF/Eden_Valley/VF_Boundary/EdenValley_site1GDA_a.shp")

fence1 <- st_read(
  "W:/VF/Eden_Valley/VF_Boundary/Fence1.shx")
fence2 <- st_read(
  "W:/VF/Eden_Valley/VF_Boundary/Fence2.shx")
fence3 <- st_read(
  "W:/VF/Eden_Valley/VF_Boundary/Fence3.shx")
fence4 <- st_read(
  "W:/VF/Eden_Valley/VF_Boundary/Fence4a.shx")
fence5 <- st_read(
  "W:/VF/Eden_Valley/VF_Boundary/Fence_hotwire_rd_side_clipped.shx")

head(Check_df_VF_week1_2_3_InclusionBord_c_animalID)
```



```{r inspect data to view quaility day1}
dim(Check_df_VF_week1_2_3_InclusionBord_c_animalID)
head(Check_df_VF_week1_2_3_InclusionBord_c_animalID,3)

Inclusion_20_05_2019 <- Check_df_VF_week1_2_3_InclusionBord_c_animalID %>% 
  filter(date == "2019-05-20") 

Inclusion_Dist20_05 <-  ggplot(Inclusion_20_05_2019, aes(x = hms, y = value, colour = collar))+
  geom_point()+
  facet_wrap(.~animal_ID)+
  geom_hline(yintercept = 0)+
  theme(axis.text.x=element_text(angle=90,hjust=1),
        legend.position = "none")+
  labs(title= "Week1 2019-05-20",
       x= "Time of day",
       y = "Distance (m) from VF")
Inclusion_Dist20_05
#ggsave(filename = "Inclusion_Dist20_05.png", device = "png" )

x_yInclusion_Dist20_05 <- ggplot() +
  geom_sf(data = eden_valley, color = "black", fill = NA) +
  geom_sf(data = fence1, color = "grey") +
  geom_sf(data = fence2, color = "grey") +
  geom_point(data = Inclusion_20_05_2019, aes(POINT_X, POINT_Y,colour = animal_ID), inherit.aes = FALSE, alpha = 0.01) +
  facet_wrap(.~animal_ID)+
  theme_bw()+
  theme(legend.position = "none",
        axis.ticks = element_blank(), axis.text.x = element_blank(), axis.text.y = element_blank())+
  labs(title= "2019-05-20")+
  xlab("") +
  ylab("") 

x_yInclusion_Dist20_05

ggsave(filename = "x_yInclusion_Dist20_05.png", device = "png" ,dpi=600)

ggplot() +
  geom_sf(data = eden_valley, color = "black", fill = NA) +
  geom_sf(data = fence1, color = "blue") +
  geom_sf(data = fence2, color = "blue") +
  geom_point(data = Inclusion_20_05_2019, aes(POINT_X, POINT_Y), inherit.aes = FALSE, alpha = 0.01) +
  #facet_wrap(.~animal_ID)+
  theme_bw()+
  theme(legend.position = "none",
        axis.ticks = element_blank(), axis.text.x = element_blank(), axis.text.y = element_blank())+
  labs(title= "2019-05-20")+
  xlab("") +
  ylab("") 



```



```{r inspect data to view quaility day2, echo=FALSE, message=FALSE, warning=FALSE}
Inclusion_21_05_2019 <- Check_df_VF_week1_2_3_InclusionBord_c_animalID %>% 
  filter(date == "2019-05-21") 

Inclusion_Dist21_05 <-  ggplot(Inclusion_21_05_2019, aes(x = hms, y = value, colour = collar))+
  geom_point()+
  facet_wrap(.~animal_ID)+
  geom_hline(yintercept = 0)+
  theme(axis.text.x=element_text(angle=90,hjust=1),
        legend.position = "none")+
  labs(title= "Week1 2019-05-21",
       x= "Time of day",
       y = "Distance (m) from VF")
Inclusion_Dist20_05
#ggsave(filename = "Inclusion_Dist21_05.png", device = "png" )

x_yInclusion_Dist21_05 <- ggplot() +
  geom_sf(data = eden_valley, color = "black", fill = NA) +
  geom_sf(data = fence1, color = "grey") +
  geom_sf(data = fence2, color = "grey") +
  geom_point(data = Inclusion_21_05_2019, aes(POINT_X, POINT_Y,colour = animal_ID), inherit.aes = FALSE, alpha = 0.01) +
  facet_wrap(.~animal_ID)+
  theme_bw()+
  theme(legend.position = "none",
        axis.ticks = element_blank(), axis.text.x = element_blank(), axis.text.y = element_blank())+
  labs(title= "2019-05-21")+
  xlab("") +
  ylab("") 

x_yInclusion_Dist21_05

ggsave(filename = "x_yInclusion_Dist21_05.png", device = "png" ,dpi=600)


ggplot() +
  geom_sf(data = eden_valley, color = "black", fill = NA) +
  geom_sf(data = fence1, color = "blue") +
  geom_sf(data = fence2, color = "blue") +
  geom_point(data = Inclusion_21_05_2019, aes(POINT_X, POINT_Y), inherit.aes = FALSE, alpha = 0.01) +
  #facet_wrap(.~animal_ID)+
  theme_bw()+
  theme(legend.position = "none",
        axis.ticks = element_blank(), axis.text.x = element_blank(), axis.text.y = element_blank())+
  labs(title= "2019-05-21")+
  xlab("") +
  ylab("") 
```

Animation giff day 1 

```{r animation for day 1}
p4a <- ggplot() +
  #ggplot() +
  geom_sf(data = eden_valley, color = "black", fill = NA) +
  geom_sf(data = fence1, color = "grey") +
  geom_sf(data = fence2, color = "grey") +
  geom_point(data = Inclusion_20_05_2019, aes(POINT_X, POINT_Y,colour = collar), inherit.aes = FALSE) +
  #facet_wrap(.~collar)+
  theme_bw()+
  theme(legend.position = "none",
        axis.text.x=element_blank(),
        axis.text.y=element_blank())


p4a  

p4b <- p4a +
  labs( title =   'Date:  {format(as_datetime(frame_time, "%b %e"), tz="GMT")}',
        #subtitle = 'Hour: {format(as_datetime(frame_time, "%H"), tz="GMT")}',
        caption = "Frame {frame} of {nframes} ({progress * 100}%)") +
  transition_time(time) +
  shadow_wake(0.3)

animation_20th <- animate(p4b, duration = 60) 
animation_20th

#anim_save(animation = animation_20th , filename = "animation_20th.gif")
```

Animation giff day 2


```{r animation for day 2}
p4a <- ggplot() +
  #ggplot() +
  geom_sf(data = eden_valley, color = "black", fill = NA) +
  geom_sf(data = fence1, color = "grey") +
  geom_sf(data = fence2, color = "grey") +
  geom_point(data = Inclusion_21_05_2019, aes(POINT_X, POINT_Y,colour = collar), inherit.aes = FALSE) +
  #facet_wrap(.~collar)+
  theme_bw()+
  theme(legend.position = "none",
        axis.text.x=element_blank(),
        axis.text.y=element_blank())


p4a  

p4b <- p4a +
  labs( title =   'Date:  {format(as_datetime(frame_time, "%b %e"), tz="GMT")}',
        #subtitle = 'Hour: {format(as_datetime(frame_time, "%H"), tz="GMT")}',
        caption = "Frame {frame} of {nframes} ({progress * 100}%)") +
  transition_time(time) +
  shadow_wake(0.3)

animation_20th <- animate(p4b, duration = 60) 
animation_20th

#anim_save(animation = animation_21th , filename = "animation_21th.gif")
```


Other days 

```{r inspect data to view quaility Vf 3, echo=FALSE, message=FALSE, warning=FALSE}
Inclusion_23_05_2019 <- Check_df_VF_week1_2_3_InclusionBord_c_animalID %>% 
  filter(date == "2019-05-23") 


x_yInclusion_Dist23_05 <- ggplot() +
  geom_sf(data = eden_valley, color = "black", fill = NA) +
  geom_sf(data = fence3, color = "grey") +
  geom_point(data = Inclusion_23_05_2019, aes(POINT_X, POINT_Y,colour = animal_ID), inherit.aes = FALSE, alpha = 0.01) +
  facet_wrap(.~animal_ID)+
  theme_bw()+
  theme(legend.position = "none",
        axis.ticks = element_blank(), axis.text.x = element_blank(), axis.text.y = element_blank())+
  labs(title= "2019-05-23")+
  xlab("") +
  ylab("") 

x_yInclusion_Dist23_05
#######################           No facet wrap #######################  
ggplot() +
  geom_sf(data = eden_valley, color = "black", fill = NA) +
  geom_sf(data = fence3, color = "blue") +
  geom_point(data = Inclusion_23_05_2019, aes(POINT_X, POINT_Y), inherit.aes = FALSE, alpha = 0.01) +
  theme_bw()+
  theme(legend.position = "none",
        axis.ticks = element_blank(), axis.text.x = element_blank(), axis.text.y = element_blank())+
  labs(title= "2019-05-23")+
  xlab("") +
  ylab("") 



ggsave(filename = "x_yInclusion_Dist23_05.png", device = "png" ,dpi=600)

Inclusion_24_05_2019 <- Check_df_VF_week1_2_3_InclusionBord_c_animalID %>% 
  filter(date == "2019-05-24") 
x_yInclusion_Dist24_05 <- ggplot() +
  geom_sf(data = eden_valley, color = "black", fill = NA) +
  geom_sf(data = fence3, color = "grey") +
  geom_point(data = Inclusion_24_05_2019, aes(POINT_X, POINT_Y,colour = animal_ID), inherit.aes = FALSE, alpha = 0.01) +
  facet_wrap(.~animal_ID)+
  theme_bw()+
  theme(legend.position = "none",
        axis.ticks = element_blank(), axis.text.x = element_blank(), axis.text.y = element_blank())+
  labs(title= "2019-05-24")+
  xlab("") +
  ylab("") 

x_yInclusion_Dist24_05

ggsave(filename = "x_yInclusion_Dist24_05.png", device = "png" ,dpi=600)

#######################           No facet wrap #######################
ggplot() +
  geom_sf(data = eden_valley, color = "black", fill = NA) +
  geom_sf(data = fence3, color = "blue") +
  geom_point(data = Inclusion_24_05_2019, aes(POINT_X, POINT_Y), inherit.aes = FALSE, alpha = 0.01) +
  theme_bw()+
  theme(legend.position = "none",
        axis.ticks = element_blank(), axis.text.x = element_blank(), axis.text.y = element_blank())+
  labs(title= "2019-05-24")+
  xlab("") +
  ylab("") 

```

fence 4


```{r inspect data to view quaility Vf 4, echo=FALSE, message=FALSE, warning=FALSE}
Inclusion_28_05_2019 <- Check_df_VF_week1_2_3_InclusionBord_c_animalID %>% 
  filter(date == "2019-05-28" & animal_ID != "NA") 


x_yInclusion_Dist28_05 <- ggplot() +
  geom_sf(data = eden_valley, color = "black", fill = NA) +
  geom_sf(data = fence4, color = "grey") +
  geom_point(data = Inclusion_28_05_2019, aes(POINT_X, POINT_Y,colour = animal_ID), inherit.aes = FALSE, alpha = 0.01) +
  facet_wrap(.~animal_ID)+
  theme_bw()+
  theme(legend.position = "none",
        axis.ticks = element_blank(), axis.text.x = element_blank(), axis.text.y = element_blank())+
  labs(title= "2019-05-28")+
  xlab("") +
  ylab("") 

x_yInclusion_Dist28_05

ggsave(filename = "x_yInclusion_Dist28_05.png", device = "png" ,dpi=600)


#######################           No facet wrap #######################
ggplot() +
  geom_sf(data = eden_valley, color = "black", fill = NA) +
  geom_sf(data = fence4, color = "blue") +
  geom_point(data = Inclusion_28_05_2019, aes(POINT_X, POINT_Y), inherit.aes = FALSE, alpha = 0.01) +
  theme_bw()+
  theme(legend.position = "none",
        axis.ticks = element_blank(), axis.text.x = element_blank(), axis.text.y = element_blank())+
  labs(title= "2019-05-28")+
  xlab("") +
  ylab("") 


Inclusion_29_05_2019 <- Check_df_VF_week1_2_3_InclusionBord_c_animalID %>% 
  filter(date == "2019-05-29"& animal_ID != "NA") 
x_yInclusion_Dist29_05 <- ggplot() +
  geom_sf(data = eden_valley, color = "black", fill = NA) +
  geom_sf(data = fence4, color = "grey") +
  geom_point(data = Inclusion_29_05_2019, aes(POINT_X, POINT_Y,colour = animal_ID), inherit.aes = FALSE, alpha = 0.01) +
  facet_wrap(.~animal_ID)+
  theme_bw()+
  theme(legend.position = "none",
        axis.ticks = element_blank(), axis.text.x = element_blank(), axis.text.y = element_blank())+
  labs(title= "2019-05-29")+
  xlab("") +
  ylab("") 

x_yInclusion_Dist29_05

ggsave(filename = "x_yInclusion_Dist29_05.png", device = "png" ,dpi=600)


#######################           No facet wrap #######################
ggplot() +
  geom_sf(data = eden_valley, color = "black", fill = NA) +
  geom_sf(data = fence4, color = "blue") +
  geom_sf(data = fence5, color = "blue") +
  geom_sf(data = fence1, color = "blue") +
  geom_sf(data = fence2, color = "blue") +
  geom_sf(data = fence3, color = "blue") +
  geom_point(data = Inclusion_29_05_2019, aes(POINT_X, POINT_Y), inherit.aes = FALSE, alpha = 0.01) +
  theme_bw()+
  theme(legend.position = "none",
        axis.ticks = element_blank(), axis.text.x = element_blank(), axis.text.y = element_blank())+
  labs(title= "2019-05-29")+
  xlab("") +
  ylab("") 

```



Other option here would be to run this analysis for days that the VF was shifted
assign colour to the  'trouble cows' and the rest are grey and see how the 'trouble cows' behaved at certain times.

#plot VF boundaries
```{r plot VF}
ggplot()+
  geom_sf(data = eden_valley, size = 2 , colour = "black", fill=NA)+
  geom_sf(data = fence1, size = 1 , colour = "black")+
  geom_sf(data = fence2, size = 1 , colour = "grey")+
  geom_sf(data = fence3, size = 1 , colour = "blue")+
  geom_sf(data = fence4, size = 1 , colour = "red")+
  geom_sf(data = fence5, size = 1 , colour = "pink")+
  coord_sf()

```

#plot of audio and pulse data


```{r bring in the audio and pulse data}
VF_week1_2_3_InclusionBord_Audio_pulse <- read_rds("download2_R_output/VF_week1_2_3_InclusionBord_Audio_pulse.rds")
```

Plot the aduio data

```{r plot the audio data}
table(VF_week1_2_3_InclusionBord_Audio_pulse$event)

VF_week1_2_3_Audio_pulse <- filter(VF_week1_2_3_InclusionBord_Audio_pulse, event != "InclusionBorder_m" )
with(VF_week1_2_3_Audio_pulse, table(event, animal_ID))
with(VF_week1_2_3_Audio_pulse, table(event, date))

VF_week1_2_3_Audio_pulse <- mutate(VF_week1_2_3_Audio_pulse,
                                   audio_pulse = case_when(
                                     event == "Audio started" ~ "Audio",
                                     event == "Audio started (short)" ~ "Audio",
                                     event == "Audio started (short) [simulated]" ~ "Audio",
                                     event == "Audio started [simulated]" ~ "Audio",
                                     event == "Pulse started" ~ "Pulse",
                                     event == "Pulse started [simulated]" ~ "Pulse"))

Aduio_sum1 <- group_by(VF_week1_2_3_Audio_pulse, date, animal_ID, audio_pulse) %>% 
  summarise(count = n())

print(Aduio_sum1)
#Aduio_sum1$day_factor <- as.factor(Aduio_sum1$day)


VF_dates=data.frame(date=as.Date(c("2019-05-20", "2019-05-23", "2019-05-28", "2019-06-03")), 
             event=c("VF1&2", "VF3", "VF4", "VF5"))
filter(Aduio_sum1, count <50) %>% 
ggplot( aes(x = date, y = count, colour = audio_pulse))+
  #geom_boxplot(alpha = 0.2)+
  geom_point()+
  theme_bw()+
  #facet_wrap(. ~ animal_ID)+
  geom_vline(data=VF_dates, mapping=aes(xintercept=date), color="blue", alpha = 0.2) +
  theme(axis.text.x=element_text(angle=90,hjust=1))+
  #,legend.position = "none")+
  labs(title= "Week1 to 3",
       x= "Date",
       y = "Counts of cues")

#can I change the date to a factor and then create a box plot?
Aduio_sum1$date_factor <- factor(Aduio_sum1$date)
table(Aduio_sum1$date_factor)
### Audio
filter(Aduio_sum1, count <50 & audio_pulse == "Audio") %>% 
#filter(Aduio_sum1, animal_ID == "Q36" & date_factor != "2019-06-06" & audio_pulse == "Audio") %>% 
#filter(Aduio_sum1, audio_pulse == "Audio") %>% 
  ggplot( aes(x = date_factor, y = count))+
  geom_boxplot(alpha = 0.2)+
  geom_point()+
  theme_bw()+
  #facet_wrap(. ~ animal_ID)+
  geom_vline(xintercept= c(1,4,9,15), colour= "blue", alpha = 0.5) +
  #geom_vline(data=VF_dates, mapping=aes(xintercept=date), color="blue", alpha = 0.2) +
  theme(axis.text.x=element_text(angle=90,hjust=1))+
  #,legend.position = "none")+
  labs(title= "",
       x= "Date",
       y = "Counts of aduio cues")
```


Pulse cues
```{r}
### pulse
#filter(Aduio_sum1, count <50 & audio_pulse == "Pulse") %>% 
filter(Aduio_sum1, audio_pulse == "Pulse") %>% 
  ggplot( aes(x = date_factor, y = count))+
  geom_boxplot(alpha = 0.2)+
  geom_point()+
  theme_bw()+
  #facet_wrap(. ~ animal_ID)+
  geom_vline(xintercept= c(1,4,9,15), colour= "blue", alpha = 0.5) +
  #geom_vline(data=VF_dates, mapping=aes(xintercept=date), color="blue", alpha = 0.5) +
  theme(axis.text.x=element_text(angle=90,hjust=1))+
  #,legend.position = "none")+
  labs(title= "",
       x= "Date",
       y = "Counts of pulse cues")

```


#Map out the exclusion data.
I have created a new varaible which is the when the animal is in the exclusion zone (ie in non grazing area)

```{r bring in the exclusion data}
VF_week1_2_3_exclusion <- read_rds("download2_R_output/VF_week1_2_3_InclusionBord_c_animalID_fill_2.rds")
```

Summaries the data based on animal and day

```{r summaries exclusion data}

event_sum <- group_by(VF_week1_2_3_InclusionBord_c_animalID_fill_2, day, animal_ID, event_number) %>% 
  summarise(max_dist = max(value), 
            mean_dis = mean(value),
            max_time = max(as_datetime(time, tz="GMT")), 
            min_time = min(as_datetime(time, tz="GMT")),
            period_time = round((time_in_exlusion_zone = max_time - min_time), digits = 1))
            
print(event_sum)
```
Plot the exclusion data

Check out the data first
seems that a few animals did not get assigned to animal ID
ac220 on the 25th around 11:00
ad3396 on the 27th around 16:19
ac213 on the 28th 06:44

I think I will need to revist step 1 

```{r inspect the exclusion data}
head(VF_week1_2_3_InclusionBord_c_animalID_fill_2)
table(VF_week1_2_3_InclusionBord_c_animalID_fill_2$animal_ID)
check_out_NA <- filter(VF_week1_2_3_InclusionBord_c_animalID_fill_2, animal_ID == "NA")
head(check_out_NA)
table(check_out_NA$collar_ID)
with(check_out_NA, table(day, collar_ID))


```
For now let just exclude the animal ID that has NA and see what we have...

```{r plot exc data}
#filter out all the data that does not have animal ID ie na and only retain exclsuion events
VF_week1_2_3_InclusionBord_c_animalID_fill_3 <- filter(VF_week1_2_3_InclusionBord_c_animalID_fill_2, animal_ID != "NA" &
                                                       event == "exclusion_zone")

head(VF_week1_2_3_InclusionBord_c_animalID_fill_2)

with(VF_week1_2_3_InclusionBord_c_animalID_fill_3, table(day, animal_ID))
#still have missing animal ID for certain days
head(VF_week1_2_3_InclusionBord_c_animalID_fill_3)
# the below is a grouping of individual animals per day per event number
event_sum_3 <- group_by(VF_week1_2_3_InclusionBord_c_animalID_fill_3, date, animal_ID, event_number) %>% 
  summarise(max_dist = max(value), 
            mean_dis = mean(value),
            max_time = max(as_datetime(time, tz="GMT")), 
            min_time = min(as_datetime(time, tz="GMT")),
            period_time = round((time_in_exlusion_zone = max_time - min_time), digits = 1))
head(event_sum_3)

#can I change the date to a factor and then create a box plot?
event_sum_3$date_factor <- factor(event_sum_3$date)

VF_dates=data.frame(date=as.Date(c("2019-05-20", "2019-05-23", "2019-05-28", "2019-06-03")), 
             event=c("VF1&2", "VF3", "VF4", "VF5"))
       
filter(event_sum_3, max_dist < 30) %>% 
#event_sum_3 %>% 
    ggplot(aes(x = date_factor, y = max_dist))+
  geom_point()+
  geom_boxplot(alpha=0.2)+
  theme_bw()+
  #facet_wrap(. ~ animal_ID)+
  #geom_vline(data=VF_dates, mapping=aes(xintercept=date), color="blue", alpha = 0.5) +
  geom_vline(xintercept= c(1,4,9,15), colour= "blue", alpha = 0.2) +
  theme(axis.text.x=element_text(angle=90,hjust=1))+
  #,legend.position = "none")+
  labs(title= "",
       x= "date",
       y = "Max distance")

################   more summary #####################
head(event_sum_3)
event_sum_3a <- group_by(event_sum_3, date, animal_ID) %>% 
  summarise(max_dist_per_animal_per_day = max(max_dist), 
            mean_dis_per_animal_per_day = mean(max_dist))
head(event_sum_3a)


event_sum_3a$date_factor <- factor(event_sum_3a$date)
event_sum_3a_subset <- filter(event_sum_3a, date < as_datetime('2019-06-01', tz="GMT"))


filter(event_sum_3a_subset, max_dist_per_animal_per_day < 20) %>% 
#event_sum_3a %>% 
    ggplot(aes(x = date_factor, y = max_dist_per_animal_per_day))+
  #geom_point()+
  geom_boxplot(outlier.shape=NA)+
  theme_bw()+
  #facet_wrap(. ~ animal_ID)+
  #geom_vline(data=VF_dates, mapping=aes(xintercept=date), color="blue", alpha = 0.5) +
  geom_vline(xintercept= c(1,4,9,15), colour= "blue", alpha = 0.2) +
  theme(axis.text.x=element_text(angle=90,hjust=1))+
  #,legend.position = "none")+
  labs(title= "",
       x= "date",
       y = "Max distance per animal per day")
head(event_sum_3a)
filter(event_sum_3a_subset, mean_dis_per_animal_per_day < 20) %>% 
#event_sum_3a %>% 
    ggplot(aes(x = date_factor, y = mean_dis_per_animal_per_day))+
  #geom_point()+
  geom_boxplot(outlier.shape=NA)+
  theme_bw()+
  #facet_wrap(. ~ animal_ID)+
  #geom_vline(data=VF_dates, mapping=aes(xintercept=date), color="blue", alpha = 0.5) +
  geom_vline(xintercept= c(1,4,9,15), colour= "blue", alpha = 0.2) +
  theme(axis.text.x=element_text(angle=90,hjust=1))+
  #,legend.position = "none")+
  labs(title= "",
       x= "date",
       y = "Mean distance per animal per day")

```


mean_dis 

```{r exl mean_dis}

  ggplot(event_sum_3, aes(x = date_factor, y = mean_dis))+
  geom_point()+
  #geom_boxplot()+
  theme_bw()+
  geom_vline(xintercept= c(1,4,9,15), colour= "blue", alpha = 0.2) +
  theme(axis.text.x=element_text(angle=90,hjust=1))+
  #,legend.position = "none")+
  labs(title= "Week1 to 3",
       x= "date",
       y = "mean distance")
```



period_time 

```{r exl period of time}

  ggplot(event_sum_3, aes(x = date_factor, y = period_time))+
  geom_boxplot()+
  theme_bw()+
  geom_vline(xintercept= c(1,4,9,15), colour= "blue", alpha = 0.2) +
  theme(axis.text.x=element_text(angle=90,hjust=1))+
  #,legend.position = "none")+
  labs(title= "Week1 to 3",
       x= "date",
       y = "period of time")
```

What about number of events per day per cow?
```{r number of events}
head(VF_week1_2_3_InclusionBord_c_animalID_fill_3)
event_sum_4 <- group_by(VF_week1_2_3_InclusionBord_c_animalID_fill_3, date, animal_ID) %>% 
  summarise(max_number_events = max(event_number))

#the number of events increment so at the end of day 06/06 we will have a total
#so what about making a new clm with animalID, Day and event number and then only retaining the unquie ones so we can count?

VF_week1_2_3_InclusionBord_c_animalID_fill_4 <- mutate(VF_week1_2_3_InclusionBord_c_animalID_fill_3,
                                                       ID_clm = paste0(animal_ID,"_", date, "_", event_number))

head(VF_week1_2_3_InclusionBord_c_animalID_fill_4)
VF_week1_2_3_InclusionBord_c_animalID_fill_4_dis <- distinct(VF_week1_2_3_InclusionBord_c_animalID_fill_4, ID_clm, .keep_all = TRUE)

event_sum_5 <- group_by(VF_week1_2_3_InclusionBord_c_animalID_fill_4_dis, date, animal_ID) %>% 
  summarise(count = n())

head(event_sum_5)
event_sum_5$date_factor <- factor(event_sum_5$date)

 ggplot(event_sum_5, aes(x = date_factor, y = count))+
  geom_point()+
  geom_boxplot(alpha = 0.2)+
  theme_bw()+
  geom_vline(xintercept= c(1,4,9,15), colour= "blue", alpha = 0.2) +
  theme(axis.text.x=element_text(angle=90,hjust=1))+
  #,legend.position = "none")+
  labs(title= "",
       x= "date",
       y = "count of events")
```



