---
title: "Step 3 graphs and options"
author: "Jackie Ouzman"
date: "12 August 2019"
output: html_document
---

```{r setup and install load packages, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)


library(tidyverse)
library(dplyr)
library(lubridate)
library(readxl)

library(ggplot2)
library(readr)
library(sp)
library(biogeo)
library(stringr)
library(rgdal)
library(sf)

library(gganimate)
library(png)
library(gifski)
```

#I need to view specfic days 
I have done this using the filter function and then check out the distance from fence.

Day 1 20/5/2019
Fence 1 and 2
Bring in the data from the data import and cleaning R markdown file

```{r load in the data, echo=FALSE, message=FALSE, warning=FALSE}
Check_df_VF_week1_2_3_InclusionBord_c_animalID <- read_rds("W:/VF/Eden_Valley/logged_VF_data/download2_R_output/df_VF_week1_2_3_InclusionBord_c_animalID_clean.rds")

eden_valley <- st_read(
  "W:/VF/Eden_Valley/VF_Boundary/EdenValley_site1GDA_a.shp")

fence1 <- st_read(
  "W:/VF/Eden_Valley/VF_Boundary/Fence1.shx")
fence2 <- st_read(
  "W:/VF/Eden_Valley/VF_Boundary/Fence2.shx")
fence3 <- st_read(
  "W:/VF/Eden_Valley/VF_Boundary/Fence3.shx")
fence4 <- st_read(
  "W:/VF/Eden_Valley/VF_Boundary/Fence4a.shx")
fence5 <- st_read(
  "W:/VF/Eden_Valley/VF_Boundary/Fence_hotwire_rd_side_clipped.shx")

head(Check_df_VF_week1_2_3_InclusionBord_c_animalID)
```



```{r inspect data to view quaility day1}
dim(Check_df_VF_week1_2_3_InclusionBord_c_animalID)
head(Check_df_VF_week1_2_3_InclusionBord_c_animalID,3)

Inclusion_20_05_2019 <- Check_df_VF_week1_2_3_InclusionBord_c_animalID %>% 
  filter(date == "2019-05-20") 

Inclusion_Dist20_05 <-  ggplot(Inclusion_20_05_2019, aes(x = hms, y = value, colour = collar))+
  geom_point()+
  facet_wrap(.~animal_ID)+
  geom_hline(yintercept = 0)+
  theme(axis.text.x=element_text(angle=90,hjust=1),
        legend.position = "none")+
  labs(title= "Week1 2019-05-20",
       x= "Time of day",
       y = "Distance (m) from VF")
Inclusion_Dist20_05
#ggsave(filename = "Inclusion_Dist20_05.png", device = "png" )

x_yInclusion_Dist20_05 <- ggplot() +
  geom_sf(data = eden_valley, color = "black", fill = NA) +
  geom_sf(data = fence1, color = "grey") +
  geom_sf(data = fence2, color = "grey") +
  geom_point(data = Inclusion_20_05_2019, aes(POINT_X, POINT_Y,colour = animal_ID), inherit.aes = FALSE, alpha = 0.01) +
  facet_wrap(.~animal_ID)+
  theme_bw()+
  theme(legend.position = "none",
        axis.text.x=element_blank(),
        axis.text.y=element_blank())+
  labs(title= "Fence 1 and 2 with data from 2019-05-20")

x_yInclusion_Dist20_05

#ggsave(filename = "x_yInclusion_Dist20_05.png", device = "png" ,dpi=600)
```



```{r inspect data to view quaility day2, echo=FALSE, message=FALSE, warning=FALSE}
Inclusion_21_05_2019 <- Check_df_VF_week1_2_3_InclusionBord_c_animalID %>% 
  filter(date == "2019-05-21") 

Inclusion_Dist21_05 <-  ggplot(Inclusion_21_05_2019, aes(x = hms, y = value, colour = collar))+
  geom_point()+
  facet_wrap(.~animal_ID)+
  geom_hline(yintercept = 0)+
  theme(axis.text.x=element_text(angle=90,hjust=1),
        legend.position = "none")+
  labs(title= "Week1 2019-05-21",
       x= "Time of day",
       y = "Distance (m) from VF")
Inclusion_Dist20_05
#ggsave(filename = "Inclusion_Dist21_05.png", device = "png" )

x_yInclusion_Dist21_05 <- ggplot() +
  geom_sf(data = eden_valley, color = "black", fill = NA) +
  geom_sf(data = fence1, color = "grey") +
  geom_sf(data = fence2, color = "grey") +
  geom_point(data = Inclusion_21_05_2019, aes(POINT_X, POINT_Y,colour = animal_ID), inherit.aes = FALSE, alpha = 0.01) +
  facet_wrap(.~animal_ID)+
  theme_bw()+
  theme(legend.position = "none",
        axis.text.x=element_blank(),
        axis.text.y=element_blank())+
  labs(title= "Fence 1 and 2 with data from 2019-05-20")
x_yInclusion_Dist21_05

#ggsave(filename = "x_yInclusion_Dist21_05.png", device = "png" ,dpi=600)
```

Animation giff day 1 

```{r animation for day 1}
p4a <- ggplot() +
  #ggplot() +
  geom_sf(data = eden_valley, color = "black", fill = NA) +
  geom_sf(data = fence1, color = "grey") +
  geom_sf(data = fence2, color = "grey") +
  geom_point(data = Inclusion_20_05_2019, aes(POINT_X, POINT_Y,colour = collar), inherit.aes = FALSE) +
  #facet_wrap(.~collar)+
  theme_bw()+
  theme(legend.position = "none",
        axis.text.x=element_blank(),
        axis.text.y=element_blank())


p4a  

p4b <- p4a +
  labs( title =   'Date:  {format(as_datetime(frame_time, "%b %e"), tz="GMT")}',
        #subtitle = 'Hour: {format(as_datetime(frame_time, "%H"), tz="GMT")}',
        caption = "Frame {frame} of {nframes} ({progress * 100}%)") +
  transition_time(time) +
  shadow_wake(0.3)

animation_20th <- animate(p4b, duration = 60) 
animation_20th

#anim_save(animation = animation_20th , filename = "animation_20th.gif")
```

Animation giff day 2


```{r animation for day 2}
p4a <- ggplot() +
  #ggplot() +
  geom_sf(data = eden_valley, color = "black", fill = NA) +
  geom_sf(data = fence1, color = "grey") +
  geom_sf(data = fence2, color = "grey") +
  geom_point(data = Inclusion_21_05_2019, aes(POINT_X, POINT_Y,colour = collar), inherit.aes = FALSE) +
  #facet_wrap(.~collar)+
  theme_bw()+
  theme(legend.position = "none",
        axis.text.x=element_blank(),
        axis.text.y=element_blank())


p4a  

p4b <- p4a +
  labs( title =   'Date:  {format(as_datetime(frame_time, "%b %e"), tz="GMT")}',
        #subtitle = 'Hour: {format(as_datetime(frame_time, "%H"), tz="GMT")}',
        caption = "Frame {frame} of {nframes} ({progress * 100}%)") +
  transition_time(time) +
  shadow_wake(0.3)

animation_20th <- animate(p4b, duration = 60) 
animation_20th

#anim_save(animation = animation_21th , filename = "animation_21th.gif")
```


Other option here would be to run this analysis for days that the VF was shifted
assign colour to the  'trouble cows' and the rest are grey and see how the 'trouble cows' behaved at certain times.



